---
title: "p8105_hw1_ym3077"
output: github_document
---

## Problem 1

Load the libraries and dataset:
```{r}
library(tidyverse)
library(moderndive)

data("early_january_weather")

```

Dataset Description:
```{r}
names(early_january_weather)
early_january_weather

nrow(early_january_weather)
ncol(early_january_weather)

mean_temp = mean(early_january_weather$temp)
mean_temp
```
The `early_january_weather` dataset contains variable: `r names(early_january_weather)`; and has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r mean(early_january_weather$temp)` °F.


Make Scatterplot:
```{r}
weather_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, 
                                                 color = humid)) + geom_point()
weather_plot
```

This weather scatterplot shows how temperature fluctuates every day, and there is an independent pattern of humidity, as low humidity periods occuring at both cold and warm temperature. 


Export the scatterplot:
```{r}
ggsave("weather_plot.png", plot = weather_plot, height = 4, width = 6)
```



## Problem 2

Create dataframe:
```{r}
hw1_df = tibble(
  random_sample = rnorm(10),
  vec_logical = rnorm(10) > 0,
  vec_character = c("Here", "is", "my", "data", "science", "one", "home", "work", "one", "answer"),
  vec_factor = factor(sample(c("A", "B", "C"), size = 10, replace = TRUE))
)
hw1_df
```

Take the mean of each variable:
```{r}
mean(hw1_df$random_sample)     
mean(hw1_df$vec_logical)        
mean(hw1_df$vec_character)
mean(hw1_df$vec_factor) 
```
We can take mean for the random sample and the logic vector, but not for character vector or factor factor. 

Convert to numeric:
```{r, echo = TRUE, results = 'hide'}
as.numeric(hw1_df$vec_logical)
as.numeric(hw1_df$vec_character)
as.numeric(hw1_df$vec_factor)
```
The **logical vector** is coerced to `1`s and `0`s, where `TRUE` becomes `1`, `FALSE` becomes `0`. This explains why taking the mean of a logical vector works: it returns the proportion of TRUE values.

The **character vector** cannot be meaningfully coerced to numbers. R returns all `NA`s with a warning. This explains why `mean()` fails for character data — it’s not numeric.

The **factor vector** is coerced to its underlying integer levels, based on the order of factor levels (e.g., "A" = 1, "B" = 2, "C" = 3 by default). This gives numeric values, and explains why `mean()` success. 

So, this coercion behavior helps explain which variables can be averaged using `mean()`, and why others cannot with errors.

