---
title: "p8105_hw1_ym3077"
output: github_document
---

## Problem 1

Load the libraries and dataset:
```{r}
library(tidyverse)
library(moderndive)

data("early_january_weather")

```

Dataset Description:
```{r}
names(early_january_weather)
early_january_weather

nrow(early_january_weather)
ncol(early_january_weather)

mean_temp = mean(early_january_weather$temp)
mean_temp
```
The `early_january_weather` dataset contains variable: `r names(early_january_weather)`; and has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

The mean temperature is `r mean(early_january_weather$temp)` °F.


Make Scatterplot:
```{r}
weather_plot = ggplot(early_january_weather, aes(x = time_hour, y = temp, 
                                                 color = humid)) + geom_point()
weather_plot
```

This weather scatterplot shows how temperature fluctuates every day, and there is an independent pattern of humidity, as low humidity periods occuring at both cold and warm temperature. 


Export the scatterplot:
```{r}
ggsave("weather_plot.png", plot = weather_plot, height = 4, width = 6)
```



## Problem 2



